Combinatorial Proofs and Decomposition Theorems for First-order Logic

### 2021-01-24 main.tex
managed to debug polar coordinate labelling of vertices; now skew bifib figure works
finished all potentially useful diagrams

%%%%%%%%% PACKAGES DOMINIC USES FOR CP FIGURES
\usepackage{tikz}
\usetikzlibrary{arrows}% e.g. >=latex' or >=stealth'
\usetikzlibrary{decorations}\usetikzlibrary{shapes.geometric}% better dot/dash in cp fibres
\usetikzlibrary{chains}% for inline skew fibrations on formulas
\usepackage{calculator}% e.g. \MULTIPLY{1.3}{4.2}{\resultmacroname} https://tug.org/TUGboat/tb33-3/tb105fuster.pdf  https://mirror.hmc.edu/ctan/macros/latex/contrib/calculator/calculator.pdf

@@

@@

>>>>

@@

%%%%%%%%% PACKAGES DOMINIC USES FOR CP FIGURES
\usepackage{tikz}
\usetikzlibrary{arrows}% e.g. >=latex' or >=stealth'
\usetikzlibrary{decorations}\usetikzlibrary{shapes.geometric}% better dot/dash in cp fibres
\usetikzlibrary{chains}% for inline skew fibrations on formulas
\usetikzlibrary{arrows}% e.g. >=latex' or >=stealth'
% \usetikzlibrary{arrows.meta}% to easily adjust arrowhead style without adjusting the line style. Problem: no Latex' or Stealth'; package is stale.
\usetikzlibrary{calc}
% %	\usetikzlibrary{decorations.markings}
\usetikzlibrary{matrix}
\usetikzlibrary{positioning}
\usepackage{calculator}% e.g. \MULTIPLY{1.3}{4.2}{\resultmacroname} https://tug.org/TUGboat/tb33-3/tb105fuster.pdf  https://mirror.hmc.edu/ctan/macros/latex/contrib/calculator/calculator.pdf

\usepackage{pifont}% for \ding http://willbenton.com/wb-images/pifont.pdf  e.g. for \cross \ding{55} which matches \checkmark or \ding{51}
\newcommand\cross{\text{\ding{55}}}

%%%%% DOMINIC: THIS IS ONLY USED FOR THE TWIN COLLAPSE EXAMPLE; PACKAGE CAN BE KILLED
%\usepackage{adjustbox}%% CONFLICT %% easier to align boxes (such as proofs) to top with, e.g. \begin{adjustbox}{valign=t,raise=-.6ex} <STUFF> \end{adjustbox} 
\usepackage{prftree}% ftp://ftp.dante.de/tex-archive/macros/latex/contrib/prftree/prftreedoc.pdf http://get-software.net/macros/latex/contrib/prftree/prftree.sty
\prflinethickness=.25pt% package default 0.2pt
\prfinterspace=1.5em% increase default space between proof rule hypotheses
\prflinepadbefore=0.2ex% default 0.3ex  above proof lines
\prflinepadafter=0ex%  default 0.3ex  below proof lines
\prflineextra=0pt% default 0.3em  proof line overhang each side

@@

\leapfig Fig.\,\ref{fig:leap} shows a fonet with a unique dualizer, and its leap graph.

Illustrating why we need to collapse twins during contraction, to preserve the target as a fograph:
%
\twincollapsepic
%
Aligning both $\singleton{}\mkern4mu\singleton[red]{}$ and
$\singleton{}\mkern4mu\singleton[blue]{}$ over
a single copy of $\forall y\mkern2mu\py$
results in two uncoloured vertices
\raisebox{2pt}[0ex][0ex]{$\column{\singleton{}\\[-1.6ex]\singleton{}}$\hspace{-2pt}}
over $\forall y$.
%
The cover therefore fails to be a fograph: both uncoloured vertices are implicitly labelled with $y$ and
so are outer $y$-binders in the scope of each other.
%
The correct operation is shown above-right,
in which the troublesome pair is collapsed to a single uncoloured vertex $\singleton{}$ over $\forall y$.
